---
title: "An Introduction to the ezADI Package"
author: "Xueyuan Cao, PhD"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{An Introduction to the ezADI Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r loadLibs, include = FALSE}
#library(MASS)
library(ezADI)
#library(ggplot2)
library(knitr)
old<- options()
data("exmpDat")
data("adi2020")
opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  digits = 3,
  tidy = FALSE,
  background = "#FFFF00",
  fig.align = 'center',
  warning = FALSE,
  message = FALSE
  )
options(width = 80, digits = 3)
#theme_set(theme_bw())
getInfo <- function(what = "Suggests") {
  text <- packageDescription("ezADI")[what][[1]]
  text <- gsub("\n", ", ", text, fixed = TRUE)
  text <- gsub(">=", "$\\\\ge$", text, fixed = TRUE)
  eachPkg <- strsplit(text, ", ", fixed = TRUE)[[1]]
  eachPkg <- gsub(",", "", eachPkg, fixed = TRUE)
  #out <- paste("\\\**", eachPkg[order(tolower(eachPkg))], "}", sep = "")
  #paste(out, collapse = ", ")
  length(eachPkg)
}
```


The **ezADI** package (short for easy area deprivation index (ADI)) contains functions to to carry out the US Census geocoder query to construct the 12-digit FIPS code for addresses, merged to ADI data downloaded from Neighborhood Atlas (please refer to \url{https://www.neighborhoodatlas.medicine.wisc.edu/}). **ezADI** loads packages as needed and assumes that they are installed. 


An example to run ezADI on example data set.
```{r exmp}
test<- ezADI(inputFile = NULL, inputDat = exmpDat, adiFile = "US_ADI_Example.csv", outputFile = NULL, batchSize = 100)
head(test$adiRes)
test$matched
test$no_match
test$problem_address[1:5]
test$nadi
options(old)
```


Install **ezADI** using

```{r install, eval = FALSE}
#devtools::install_github('xueyuancao/ezADI', dependencies = c("Depends", "Suggests"))
```